---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# rcr

rcr is an R package to calculate a basic backwater profile for open channels using the standard step method.

The package is currently configured for backwater calculations with the subcritical assumption in open channels only,
supercritical and mixed regimes, and hydrualic structures, will be added in future versions.

## Installation

You can install rcr from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("rchlumsk/rcr")
```

## rcr Wishlist

Any issues or feature requests can be submitted on Github via the Issues tab. You may also submit feature requests directly to Robert Chlumsky (rchlumsk@uwaterloo.ca) via email.

## Examples 

See the vignettes in the package for examples of using the package functions using the sample data provided with the package.
