---
title: "River Computations in R (rcr-package) Demonstration"
author: "R. Chlumsky"
date: "May 2019"
output: pdf_document
urlcolor: blue
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## rcr Demonstration

A demonstration of the **rcr** package using the built-in sample data is provided.

Read in the sample package cross-section data.

```{r}
library(rcr)

# read in geometry for two sections
df <- rcr::topo_sections
dd_4 <- df[df$xsection == 4,]
dd_5 <- df[df$xsection == 5,]
dd_6 <- df[df$xsection == 6,]
```

Setup the boundary conditions and rcr options object.

```{r}
Q <- 9.5  # cms
bc_4 <- bc(station=4,reach="Reach1_Name",location="Downstream",bctype="Normal Depth",bcvalue=0.012)
ropt <- rcr_options() # use default rcr_options values

```

Assign the geometries for three cross-sections.

```{r}
xs_4 <- xsection(riverstation="4",station=0,xx=dd_4$xx,zz=dd_4$zz,Manning=dd_4$nn,
                 Manning_LOB=0.05,Manning_Main=0.035,Manning_ROB=0.05,
                 lbs_xx=5.13,rbs_xx=11.12,
                 ds_length_LOB=230,ds_length_Main=230,ds_length_ROB=230,contraction_coeff=0.1,expansion_coeff=0.3)

xs_5 <- xsection(riverstation="5",station=58,xx=dd_5$xx,zz=dd_5$zz,Manning=dd_5$nn,
                 Manning_LOB=0.05,Manning_Main=0.035,Manning_ROB=0.05,
                 lbs_xx=4.52,rbs_xx=13.36,
                 ds_length_LOB=60,ds_length_Main=58,ds_length_ROB=64,contraction_coeff=0.1,expansion_coeff=0.3)

xs_6 <- xsection(riverstation="6",station=80,xx=dd_6$xx,zz=dd_6$zz,Manning=dd_6$nn,
                 Manning_LOB=0.045,Manning_Main=0.035,Manning_ROB=0.05,
                 lbs_xx=1.7,rbs_xx=8.93,
                 ds_length_LOB=22,ds_length_Main=22,ds_length_ROB=28,contraction_coeff=0.1,expansion_coeff=0.3)

```

Create the geometries from xsection object, and calculate the hydraulic outputs.

```{r}
# create new geometry under variable g02 from two cross-sections
g02 <- geom$new(xsectionList=list(xs_4,xs_5,xs_6),geomname="Existing Condition 20190121")

# check order of g02 items, sort by g02$xsectionList[[1]]$station
g02$xsectionList[[1]]$station

# run hydraulic analysis and check results
hydraulic_output <- rcr::compute_profile(geometry=g02,Q=9.59,boundary_conditions=bc_4,options=ropt)
names(hydraulic_output) # calculated fields
head(hydraulic_output[,1:8]) # truncated output for demo pdf
```
Change the parameters in the ropt object, and re-run the calculation.

```{r}
ropt$silent_cp <- TRUE # silence the compute_profile output
ropt$silent_nd <- TRUE # silence the normal_depth output
ropt$dx <- 0.01        # change the interpolated horizontal chainage to 5cm, more coarse resolution

hydraulic_output <- rcr::compute_profile(geometry=g02,Q=9.59,boundary_conditions=bc_4,options=ropt)
head(hydraulic_output[,1:8]) # truncated output for demo pdf
```

Use some of the other tools, such as calculating the flow area or the bankfull flow.
```{r}
# estimate bankfull flow for xsection #4; default wsl is lowest defined bank height
bankfull_flow(xs=xs_4,S=0.001,wsl=NA,ropt)

# or for a presribed water surface level
bankfull_flow(xs=xs_4,wsl=176.0,S=0.001,ropt)

# calculate flow areas for specific segments
flow_area(xs=xs_4,wsl=176,stns=c(3,5,7,10),ropt)
```

Modify the geometry with a list an additional cross-section.
```{r}
num_xsections <- length(g02$xsectionList)
g02$xsectionList[[(num_xsections+1)]] <- xs_6 # add one item more to list
g02$xsectionList[[4]]$riverstation <- "7"
```

Run multiple flow profiles with new geometry (use wrapper function compute_flow_profiles).
```{r}
hydraulic_outputs <- compute_flow_profiles(geometry=g02,flows=seq(5,20,5),boundary_conditions=bc_4,options=ropt)
head(hydraulic_outputs[,1:8]) # truncated output for demo pdf
```

